### 2016-04-21 ch03-lrm/lrm-paper.tex
Some TODOfigs

\begin{itemize}
    \item \TODO{choice $s$ or $z$}
    \item \TODO{bounds RMSE, Bias, StdDev}
    \item \TODO{derivation Bias}
    \item \TODO{comparison LPM/LRM}
      \begin{itemize}
        \item \TODO{Good LPM window}
        \item \TODO{Good LRM window}
      \end{itemize}
    \item \TODO{influence of noise filter: mismatch with model}
    \item \TODO{comparison LRM/LRik (LBTLS)}
\end{itemize}

@@

\subsection{The Local Rational Method with Iterative Cost}

\TODO{define local cost}
\TODO{define local design matrix}

@@

\section{Order selection}
Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
In particular~\citep{Pintelon2010LPM1}:
\begin{equation}
\order{C} \leq \max\set{\order{B},\order{A}}
\end{equation}
 and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that 
 \begin{equation}
 \nWind \geq \order{B} + \order{A} + \order{C} + 2
 \text{.}
 \end{equation}

Different heuristics exist to select the local bandwidth $\nWind$, e.g.~\citet{Fan1995,Thummala2012LPMBW,Stenman2000ASETFE} in the framework of local modeling approaches.
As such, we focus mainly on the selection of the model order hyper-parameters ($\order{A}$, $\order{B}$ and $\order{C}$) for a fixed value of $\nWind$.

Here, we take an approach that decides amongst a group of candidate models $\Set{M_1, \ldots, M_N}$, which model $M_i$ is the best model according to some criterion: i.e. one that captures that system dynamics but remains parsimonious.
To do so, one needs to define a criterion that both takes `goodness-of-fit' (e.g. value of the cost function, $R^2$, \ldots) and model complexity into account to ensure that the model captures only the systematic behavior and not random variations of the particular measurement.
The latter is often done using `cross-validation'.

In statistical learning, many relevant cross-validation approaches exist.
Within the system identification community a few simple approaches have been widely adopted~\citep[Chapter 11]{Pintelon2012} to ensure that one does not overmodel the data.
In the following, a short overview is given of different approaches.

\paragraph{Plug-in methods}
In plug-in methods, a goodness-of-fit criterion (e.g. the log-likelihood function $\LogLikelihood$ of the estimated model $M$ given the estimation dataset $Z$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
E.g. a common choice is the \gls{AIC}~\citep{Akaike1974} or the \gls{AICc}~\citep{Hurvich1989}, which are defined as
\begin{align}
L_{\mathrm{\AIC}} &=
 - 2  \loglikelihood{M | Z} 
 + 2 \nth\\
L_{\mathrm{\AICc}} &= 
- 2  \loglikelihood{M | Z} 
+   \frac{2 \nth\nWind}{\nWind - \nth - 1}
\end{align}
where $\nth$ is the number of  estimated parameters in the model $M(\theta)$.
In the context of local modeling, the \gls{AIC} is a poor choice since it relies on asymptotic arguments of the data set, i.e. $\nWind \to \infty$, which is obviously an unwarranted choice in this context.
The best model among a set of $q$ possible models $\Set{M_1, \ldots, M_q}$ is then
\begin{equation}
  M_{\star} \isdef 
  \arg_{M} \min 
  \Set{
    L_{\mathrm{AIC(c)}}(M)
  }
  \text{,}
\end{equation}
which is the only model that is hence retained.

\begin{remark}
It should be noted that due to $\loglikelihood{M | Z}$ , the value of $L_{\mathrm{AIC(c)}}(M,Z)$ is inherently coupled with the particular dataset $Z$.
Practically, this means that such criteria can only be used to compare local models that are estimated from the same local dataset (i.e. they have the same $\nWind$ and center frequency).
Consequently, the \gls{AICc} criterion cannot be used to select a proper $\nWind$.
\end{remark}

\paragraph{Holdout method}
The so-called `holdout' cross-validation method ensures a good model by first splitting the dataset into two smaller disjoint datasets: e.g. $70\%$ of the data  is used to estimate the model and a goodness-of-fit criterion (e.g. cost function) is used on the remaining data to determine which model has the best out-of-sample performance.
By using independent datasets and assessing the performance of the model on (unseen) validation data, overfitted models can be rejected.

\begin{remark}
Unfortunately, these typical approaches either assume that an abundantly large dataset is available or  assume the models are estimated on  a fixed dataset.
As such, these methods are not ideal for local modeling where the (local) dataset is rather small by design and could change by means of the local bandwidth $N_W$.
\end{remark}

\paragraph{Leave-out cross-validation}
Instead, we use a better-suited cross-validation approach known as \gls{LOOCV} that is related to the \gls{AIC}~\citep{Stone1977}.
Plainly, \gls{LOOCV} cross-validates the model by in turn leaving out each data point, estimating the local model parameters and observing the difference between the omitted data point and the estimate.
In effect, such an approach calculates the \gls{PRESS} for each local model:
\begin{equation}
 \PRESS = 
 \frac{1}{\nWind} 
  \sum_{r \in \LocalShifts{}}
    \abs{\ignoring{r}{\LocalVector{E}}}^2
    \text{,}
\label{eq:PRESS-general}
\end{equation}
where $\ignoring{r}{\LocalVector{E}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\estimated{Y}}}$, i.e. the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.
To select the best model from a set of candidate models, only the model with the lowest \gls{PRESS} value is retained.
In general, this means that \gls{LOOCV} requires estimating $\nWind$ additional models (one for each omitted data point) and hence can be very time-consuming.

For linear models (i.e. $\LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta}$, such as for the \gls{LRM} and \gls{LPM}), however, the \gls{PRESS} can be calculated in a single step without estimating any additional models~\citep[Sec.~12.3.2]{Seber2003}:
\begin{equation}
\PRESS = \frac{\LocalVector{E}^{\HT} \LocalVector{W}^{-1} \LocalVector{E}}{2N_W + 1}
\end{equation}
where $\LocalVector{E}$ is the residual vector of the full estimation and $\LocalVector{W}$ is a diagonal weighting matrix with $\LocalVector{W}_{ii} = (1 - \LocalVector{H}_{ii})^{\HT} (1 - \LocalVector{H}_{ii})$ and
$\LocalVector{H} = \LocalMatrix{K} \pinv{\LocalMatrix{K}}$ is the so-called `hat-matrix' that is known to be idempotent.

@@

\TODO{SNR}
The \gls{SNR} in the system bandwidth $\BW$ is defined as
\begin{equation}
  \SNR_{\BW} \isdef
  \frac{\int_{\BW} \abs{Y_0(\omega)}^2 \dd{\omega}}
            {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
\end{equation}
where $\BW$ is the frequency range of the $3 \unit{dB}$ bandwidth of the system, i.e. where $\abs{G_0} \geq \norm[\infty]{\true G} - 3 \unit{dB}$.

\TODO{plot example spectrums}

@@

\TODO{insert figure: Y(Y,E,T) vs freq}
\TODO{insert figure: err vs SNR}
\paragraph{Noiseless case}
In the noiseless case, one can observe the approximation error that is made by using the \gls{LRM}, \gls{LPM} and \gls{ETFE}.
For the \gls{ETFE}, it can be seen that the error is very high.
This can be expected since the \gls{ETFE} does not separate transient and leakage contributions.
this error only disappears very slowly by measuring a longer record due to the presence of the leakage term.
As such, 
\TODO{figure: RMS, bias, std voor inf SNR}

\TODO{figure: RMS, bias, std voor high SNR}
\TODO{figure: RMS, bias, std voor 20 dB SNR}
\TODO{figure: RMS, bias, std voor 10 dB SNR}

>>>>

\begin{itemize}
    \item \TODO{choice $s$ or $z$}
    \item \TODO{derivation Bias}
      \begin{itemize}
        \item \TODO{Good LPM window}
        \item \TODO{Good LRM window}
      \end{itemize}
    \item \TODO{influence of noise filter: mismatch with model}
\end{itemize}

@@

\TODO{define notations for LPM etc.}

@@

@@

The \gls{SNR} in the system bandwidth $\BW$ is defined as
\begin{equation}
  \SNR_{\BW} \isdef
  \frac{\int_{\BW} \abs{Y_0(\omega)}^2 \dd{\omega}}
            {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
\end{equation}
where $\BW$ is the frequency range of the $3 \unit{dB}$ bandwidth of the system, i.e. where $\abs{G_0} \geq \norm[\infty]{\true G} - 3 \unit{dB}$.

\TODO{plot example spectrums}
\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[Example spectra]
  \label{fig:nparam:spectra}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[Y(Y,E,T) vs freq of single simulation]
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[RMSE, var, bias for (SNR, NBW) over freq]
\end{figure}

\TODO{describe aggregation over $\omega$}

\paragraph{Noiseless case}
In the noiseless case, one can observe the approximation error that is made by using the \gls{LRM}, \gls{LPM} and \gls{ETFE}.
For the \gls{ETFE}, it can be seen that the error is very high.
This can be expected since the \gls{ETFE} does not separate transient and leakage contributions.
this error only disappears very slowly by measuring a longer record due to the presence of the leakage term.
As such, \TODO{afschrijven}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[ RMS, bias, std for $\SNR = \infty$]
  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in a relative approximation error of $-100\unit{dB}$.}
  \label{fig:nparam:comparison:noiseless}
\end{figure}

\paragraph{Good signal-to-noise ratios}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[ RMS, bias, std for $\SNR = 60\unit{dB}$]
  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system. A relative approximation error of $-100 \unit{dB}$ is observed.}
  \label{fig:nparam:comparison:hiSNR}
\end{figure}

\paragraph{Poor signal-to-noise ratios}
\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[ RMS, bias, std for $\SNR = 20\unit{dB}$]
  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$. The \gls{LRM} outperforms the \gls{LPM}.}
  \label{fig:nparam:comparison:lowSNR}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[ RMS, bias, std for $\SNR = 10\unit{dB}$]
  \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$. An approximation error of $-100 \unit{dB}$ is observed.}
  \label{fig:nparam:comparison:terribleSNR}
\end{figure}

\begin{guideline}{For resonant systems, use the LRM when $\SNR \geq 20 \unit{dB}$}
\end{guideline}

\begin{guideline}{For long measurements, the choice of local modeling method does not matter}
\end{guideline}

\begin{remark}
In all the simulations, it can be seen that for $\nWind \to \infty$, the error tapers off.
\TODO{andere pieken gaan in de praktijk alles om zeep helpen en dus bovengrens stellen}
\end{remark}

### 2016-04-21 ch03-lrm/nonparametric.tex
LRM: part of bias, some intro
Lots of work on CH03
Some TODOfigs

\chapter{Non-parametric modeling}
\def\thisDir{ch03-lrm}
\tikzsetfigurename{ch03fig}
\label{sec:nonparametric}

@@

\section{\TODO{LPM}}
\section{\TODO{LRM}}
\input{\thisDir/lrm-paper.tex}

@@

\section{\TODO{Bias-variance trade-off }}
\TODO{import LRM paper}

\subsection{\TODO{Tuning rules}}
\subsubsection{\TODO{Tuning using an Oracle}}
\subsubsection{\TODO{Cross-validation}}

\subsection{\TODO{Application}}

\subsubsection{\TODO{AVIS}}
% \subsubsection{\TODO{F16}}

>>>>

\chapter{Non-parametric Modeling}
\def\thisDir{ch03-lrm}
\tikzsetfigurename{ch03fig}
\label{sec:nonparametric}
% \myEpigraph{}{}{}

@@

\input{\thisDir/lrm-paper.tex}

\section{Trading off the bias and variance}

\subsection{Order selection}
Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
In particular~\citep{Pintelon2010LPM1}:
\begin{equation}
\order{C} \leq \max\set{\order{B},\order{A}}
\end{equation}
 and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that 
 \begin{equation}
 \nWind \geq \order{B} + \order{A} + \order{C} + 2
 \text{.}
 \end{equation}

Different heuristics exist to select the local bandwidth $\nWind$, e.g.~\citet{Fan1995,Thummala2012LPMBW,Stenman2000ASETFE} in the framework of local modeling approaches.
As such, we focus mainly on the selection of the model order hyper-parameters ($\order{A}$, $\order{B}$ and $\order{C}$) for a fixed value of $\nWind$.

Here, we take an approach that decides amongst a group of candidate models $\Set{M_1, \ldots, M_N}$, which model $M_i$ is the best model according to some criterion: i.e. one that captures that system dynamics but remains parsimonious.
To do so, one needs to define a criterion that both takes `goodness-of-fit' (e.g. value of the cost function, $R^2$, \ldots) and model complexity into account to ensure that the model captures only the systematic behavior and not random variations of the particular measurement.
The latter is often done using `cross-validation'.

In statistical learning, many relevant cross-validation approaches exist.
Within the system identification community a few simple approaches have been widely adopted~\citep[Chapter 11]{Pintelon2012} to ensure that one does not overmodel the data.
In the following, a short overview is given of different approaches.

\paragraph{Plug-in methods}
In plug-in methods, a goodness-of-fit criterion (e.g. the log-likelihood function $\LogLikelihood$ of the estimated model $M$ given the estimation dataset $Z$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
E.g. a common choice is the \gls{AIC}~\citep{Akaike1974} or the \gls{AICc}~\citep{Hurvich1989}, which are defined as
\begin{align}
L_{\mathrm{\AIC}} &=
 - 2  \loglikelihood{M | Z} 
 + 2 \nth\\
L_{\mathrm{\AICc}} &= 
- 2  \loglikelihood{M | Z} 
+   \frac{2 \nth\nWind}{\nWind - \nth - 1}
\end{align}
where $\nth$ is the number of  estimated parameters in the model $M(\theta)$.
In the context of local modeling, the \gls{AIC} is a poor choice since it relies on asymptotic arguments of the data set, i.e. $\nWind \to \infty$, which is obviously an unwarranted choice in this context.
The best model among a set of $q$ possible models $\Set{M_1, \ldots, M_q}$ is then
\begin{equation}
  M_{\star} \isdef 
  \arg_{M} \min 
  \Set{
    L_{\mathrm{AIC(c)}}(M)
  }
  \text{,}
\end{equation}
which is the only model that is hence retained.

\begin{remark}
It should be noted that due to $\loglikelihood{M | Z}$ , the value of $L_{\mathrm{AIC(c)}}(M,Z)$ is inherently coupled with the particular dataset $Z$.
Practically, this means that such criteria can only be used to compare local models that are estimated from the same local dataset (i.e. they have the same $\nWind$ and center frequency).
Consequently, the \gls{AICc} criterion cannot be used to select a proper $\nWind$.
\end{remark}

\paragraph{Holdout method}
The so-called `holdout' cross-validation method ensures a good model by first splitting the dataset into two smaller disjoint datasets: e.g. $70\%$ of the data  is used to estimate the model and a goodness-of-fit criterion (e.g. cost function) is used on the remaining data to determine which model has the best out-of-sample performance.
By using independent datasets and assessing the performance of the model on (unseen) validation data, overfitted models can be rejected.

\begin{remark}
Unfortunately, these typical approaches either assume that an abundantly large dataset is available or  assume the models are estimated on  a fixed dataset.
As such, these methods are not ideal for local modeling where the (local) dataset is rather small by design and could change by means of the local bandwidth $N_W$.
\end{remark}

\paragraph{Leave-out cross-validation}
Instead, we use a better-suited cross-validation approach known as \gls{LOOCV} that is related to the \gls{AIC}~\citep{Stone1977}.
Plainly, \gls{LOOCV} cross-validates the model by in turn leaving out each data point, estimating the local model parameters and observing the difference between the omitted data point and the estimate.
In effect, such an approach calculates the \gls{PRESS} for each local model:
\begin{equation}
 \PRESS = 
 \frac{1}{\nWind} 
  \sum_{r \in \LocalShifts{}}
    \abs{\ignoring{r}{\LocalVector{E}}}^2
    \text{,}
\label{eq:PRESS-general}
\end{equation}
where $\ignoring{r}{\LocalVector{E}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\estimated{Y}}}$, i.e. the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.
To select the best model from a set of candidate models, only the model with the lowest \gls{PRESS} value is retained.
In general, this means that \gls{LOOCV} requires estimating $\nWind$ additional models (one for each omitted data point) and hence can be very time-consuming.

For linear models (i.e. $\LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta}$, such as for the \gls{LRM} and \gls{LPM}), however, the \gls{PRESS} can be calculated in a single step without estimating any additional models~\citep[Sec.~12.3.2]{Seber2003}:
\begin{equation}
\PRESS = \frac{\LocalVector{E}^{\HT} \LocalVector{W}^{-1} \LocalVector{E}}{2N_W + 1}
\end{equation}
where $\LocalVector{E}$ is the residual vector of the full estimation and $\LocalVector{W}$ is a diagonal weighting matrix with $\LocalVector{W}_{ii} = (1 - \LocalVector{H}_{ii})^{\HT} (1 - \LocalVector{H}_{ii})$ and
$\LocalVector{H} = \LocalMatrix{K} \pinv{\LocalMatrix{K}}$ is the so-called `hat-matrix' that is known to be idempotent.

@@

\input{\thisDir/proofLOOCV.tex}

### 2016-04-21 ch05-initvals/initial-values.tex
Some TODOfigs

  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $N_W=3$, such that
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
\true{G}(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in \LocalShifts[]$ with $\LocalShifts[] = \{-N_W,-N_W+1,\dots,B_W\}$ and $N_W$ is a tunable parameter. 
%TODO notation LPM uniform maken met CH03/CH04

  The \gls{LPM} estimate of the \gls{FRF} at frequency index $k$ is the first estimated local parameter, \emph{viz}:
\begin{equation}
\hat{G}_\text{LPM}(\Omega_k) = \hat{G}_k
\text{.}
\end{equation}
This procedure is repeated for all $k$ in the frequency band of interest.

\emph{Impulse response truncation}. 
The estimate is smoothed further by truncating its impulse response function $g_{\LPM}(t) = \mathrm{IDFT}\, \left( \hat{G}_{\LPM}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation}.

@@

To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of $\abs{g_{\LPM}(t)}$ using a linear least-squares approach.
Then, $\truncTime$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
\begin{equation}
  \truncTime = \min \Set{ t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g  }
  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
  \text{,}
\end{equation}
where $\gamma=1$ was used in this chapter for simplicity.
By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated \gls{FRF} $G_{\trunc}(\Omega_k) = \mathrm{DFT} \left( g_{\trunc}(t)\right)$ further.
This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.

@@

The $\mathcal{L}_2$ norm used in equation \eqref{eq:successrateTol} is defined~\citep{Skogestad2005} as
\begin{align}
\norm[2]{G(z)} &\isdef \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}& \text{ for discrete time,}\\
\norm[2]{G(s)} &\isdef \sqrt{\frac{1}{2\pi}\int_{-\infty}^{+\infty} |G(j\omega)|^2\ \mathrm{d}\omega}& \text{ for continuous time}
\end{align}
 which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in \secref{sec:initial-values:CompuSR}.

>>>>

  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $N_W=3$, such that
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
\true{G}(\omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\omega_{k+r})&\approx T(\omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in \LocalShifts[]$ with $\LocalShifts[] = \{-N_W,-N_W+1,\dots,B_W\}$ and $N_W$ is a tunable parameter. 
%TODO notation LPM uniform maken met CH03/CH04

  The \gls{LPM} estimate of the \gls{FRF} at frequency index $k$ is the first estimated local parameter, \emph{viz}:
\begin{equation}
\hat{G}_\text{LPM}(\omega_k) = \hat{G}_k
\text{.}
\end{equation}
This procedure is repeated for all $k$ in the frequency band of interest.

\emph{Impulse response truncation}. 
The estimate is smoothed further by truncating its impulse response function $g_{\LPM}(t) = \IDFT \left( \hat{G}_{\LPM}(\omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation}.

@@

To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of $\abs{g_{\LPM}(t)}$ using a linear least-squares approach.
Then, $\truncTime$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
\begin{equation}
  \truncTime = \min \Set{ t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g  }
  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
  \text{,}
\end{equation}
where $\gamma=1$ was used in this chapter for simplicity.
By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated \gls{FRF} $G_{\trunc}(\omega_k) = \DFT \left( g_{\trunc}(t)\right)$ further.
This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.

@@

The $\mathcal{L}_2$ norm used in equation \eqref{eq:successrateTol} is defined~\citep{Skogestad2005} as
\begin{align}
\norm[2]{G(z)} &\isdef \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}& \text{ for discrete time,}\\
\norm[2]{G(s)} &\isdef \sqrt{\frac{1}{2\pi}\int_{-\infty}^{+\infty} |G(j\omega)|^2\ \mathrm{d}\omega}& \text{ for continuous time}
\end{align}
 which, in practice, is computed by using the adaptive global quadrature algorithm provided by the \MATLAB function \code{integral}.
The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in \secref{sec:initial-values:CompuSR}.
